% !TeX spellcheck = en_GB
\thispagestyle{firststyle}
We're really happy that you're starting your studies in \studiengang in Tübingen!
To facilitate your start to your studies, we want to provide you with some information which will help you get through the first weeks.

Who or what is this \glqq student council\grqq? We, the student council of computer science, are a group of students from the subjects computer science, bioinformatics, media computer science, cognitive science, medical informatics, and machine learning
who commit themselves to the students' interests. Our work includes, on one hand, the representation of students in university bodies, on the other hand, we try to facilitate the university lives of our fellow students (i.e. beginners care,
events, mentoring, and so on).

\ifmaster
    \ifml
We recommend participating at our beginners events because the transition to master's studies or from another university respectively often proves to be difficult. This way you get a first look into everyday life in Tübingen.
    \fi
\fi
At our events, there will be many students in higher semesters who are eagerly awaiting to answer all your questions. You can find an overview of our events on the following pages.

In case you have questions before or after our events, you can reach us by mail at \texttt{fsi\At fsi.uni-tuebingen.de}
On our home page
\url{https://www.fsi.uni-tuebingen.de} you can already find helpful information about your studies. If you're interested in collaborating with the student council, just come to one of our meetings! The current date will be published on our web page.

We're excited to meet you at our beginners events!\\
%\vfill
Your student council of computer science
\par\hfill{\footnotesize Editors: Anita \& Samuel}
\vfill

% \noindent\makebox[\textwidth][c]{%
% 	\setlength{\fboxrule}{4pt}
% 	\fcolorbox{green}{white}{
% 		\begin{minipage}[t]{
% 				\textwidth}
% 			If you aren't vaccinated yet, then you can get a vaccination in the special programme of the university.\\
% 			More information can be found on \url{https://uni-tuebingen.de/universitaet/infos-zum-coronavirus/impfen/} or \url{https://dranbleiben-bw.de}.
% \end{minipage}}}
